### 2014-03-04 seminar/seminar_report/chapter3.tex
changes

Web services come with different quality of service parameters.
These parameters include availability, reliability, successability, throughput, latency, capacity, cost, regulatory and security\cite{DBLP:conf/smc/Al-MasriM09a}.
We adopted a real world dataset \cite{DBLP:conf/smc/Al-MasriM09a}
which has aggregated and normalized each of these parameters to a
real value between 0 and 1. Since requests are not shared among
web services and are distributed among all of them inside a
community, each one of them comes with a given QoS denoted by
$(QoS_{ws})$. We assume that $(QoS_{ws})$ is obtained by a certain linear weight function of the parameters. We use this quality output later in evaluating the
community \emph{worth} or \emph{payoff} function.

>>>>

Web services come with different quality of service parameters.
These parameters include availability, reliability, successability, throughput, latency, capacity, cost, regulatory and security\cite{DBLP:conf/smc/Al-MasriM09a}\footnote[1]{The implemented environment includes the QWS dataset by Eyhab Al-Masri and Qusay H. Mahmoud freely available at: http://www.uoguelph.ca/\textasciitilde{}qmahmoud/qws/.}.
We adopted a real world dataset \cite{DBLP:conf/smc/Al-MasriM09a}
which has aggregated and normalized each of these parameters to a
real value between 0 and 1. Since requests are not shared among
web services and are distributed among all of them inside a
community, each one of them comes with a given QoS denoted by
$(QoS_{ws})$. We assume that $(QoS_{ws})$ is obtained by a certain linear weight function of the parameters. We use this quality output later in evaluating the
community \emph{worth} or \emph{payoff} function.

### 2014-03-04 seminar/seminar_report/chapter5.tex
changes

\begin{itemize}
\item Analyzing other cooperative solution concepts such as Kernel
and Nucleolus where payoff division is guaranteed to exist and may
have optimal results.

\item Analyzing the impact of Q-learning and reinforcement
learning on the performance of our model.

\item Developing a community membership algorithm technique for
our agents in more distributed and "incomplete information" settings.

%\item Developing an open source, Java based Tool, with UI for
%solving Core and Shapely solution concepts based on different
%input valuation functions.
\end{itemize}

\begin{center}
    \begin{tabular}{ | l | l | p{5cm} |}
    \hline
    Term & Activity & Publication \\ \hline
    Winter 2014 & 1 & 1 \\ \hline
    Summer 2014 & 1 & 1 \\ \hline
    Fall 2014 & 1 & 1 \\ \hline
    Winter 2015 & 1 & 1 \\
    \hline
    \end{tabular}
\end{center}

@@

    \begin{enumerate}
        \item E. Khosrowshahi Asl, J. Bentahar, H. Otrok, R. Mizouni, \emph{``Efficient Community Formation for Web Services.''} Accepted at IEEE Transactions on Services Computing, Feb. 2014, IEEE. (Impact factor: 2.46)
        \item E. Khosrowshahi Asl, J. Bentahar, R. Mizouni, B. Khosravifar, H. Otrok, \emph{``To Compete or to Cooperate? This is the Question in Communities of Autonomous Services.''} In the Journal of Expert Systems and Applications, Feb. 2014, Elsevier. (Impact factor: 1.854, 5-year:  2.339)
        \item Published a conference paper in 10th IEEE International Conference on Services Computing; \emph{``Efficient Coalition Formation for Web Services''}, 2013
        \item Published a conference paper to the 10th International Conference on Service Oriented Computing; \emph{``Analyzing Coopetition Strategies of Services within Communities''}, 2012
    \end{enumerate}

>>>>

\begin{itemize}
\item \textbf{Winter 2014: }Analyzing other cooperative solution concepts such as Kernel
and Nucleolus where payoff division is guaranteed to exist and may
have optimal results.

\item \textbf{Summer 2014: }Analyzing the impact of Q-learning and reinforcement
learning on the performance of our model.

\item \textbf{Fall 2014: }Developing a community membership algorithm technique for
our agents in more distributed and ``incomplete information'' settings.

\item \textbf{Winter 2015: }Thesis work and PhD Defense.
%\item Developing an open source, Java based Tool, with UI for
%solving Core and Shapely solution concepts based on different
%input valuation functions.
\end{itemize}

%\begin{center}
%    \begin{tabular}{ | l | l | p{5cm} |}
%    \hline
%    Term & Activity & Publication \\ \hline
%    Winter 2014 & 1 & 1 \\ \hline
%    Summer 2014 & 1 & 1 \\ \hline
%    Fall 2014 & 1 & 1 \\ \hline
%    Winter 2015 & 1 & 1 \\
%    \hline
%    \end{tabular}
%\end{center}

@@

    \begin{enumerate}
        \small{
        \item E. Khosrowshahi Asl, J. Bentahar, H. Otrok, R. Mizouni, \emph{``Efficient Community Formation for Web Services.''} Accepted at IEEE Transactions on Services Computing, Feb. 2014, IEEE. (Impact factor: 2.46)
        \item E. Khosrowshahi Asl, J. Bentahar, R. Mizouni, B. Khosravifar, H. Otrok, \emph{``To Compete or to Cooperate? This is the Question in Communities of Autonomous Services.''} In the Journal of Expert Systems and Applications, Feb. 2014, Elsevier. (Impact factor: 1.854, 5-year:  2.339)
        \item E. Khosrowshahi Asl, J. Bentahar, H. Otrok, R. Mizouni, \emph{``Efficient Coalition Formation for Web Services. In the 10th''} IEEE  International Conference on Services Computing (SCC 2013), Santa Clara Marriott, CA, USA, June 27-July 2, 2013
        \item B. Khosravifar, M. Alishahi, E. Khosrowshahi Asl, J. Bentahar, R. Mizouni, H. Otrok, \emph{``Analyzing Coopetition Strategies of Services within Communities''}. In the 10th International Conference on Service Oriented Computing, (ICSOC 2012), Shanghai, China, Nov. 2012
        }
    \end{enumerate}
